We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-02 paper/paper.tex
+1 paragraph

This corresponds to a pair number density of $8 \times10^{-6}$ pairs
Mpc$^{-3}$, this is a factor $2.4$ lower than the pair number density
we find in Illustris-1.
There were a total of 146 pairs that met those criteria, but only $12$
were chosen for resimulation. 
Additionally, the selected pairs have a relative tangential velocity
less than $75$ \kms.

@@

We compare every satellite distribution against its own spherically
randomized distribution.
We keep fixed the radial position of every satellite
with respect to the central galaxy and then randomizing its angular
position. 
We repeat this procedure 1000 times for each satellite distribution
and proceed to measure the quantities mentioned in the last section:
$w$, $c/a$, $b/a$ and $mu$.
For each quantity we compute an average and standard deviation from
the 1000 random samples. 
This allows us to build a normalized version of all quantities of
interest by substracting the mean and dividing between the standard
deviation of the randomized samples.

@@

@@

\section{Discussion}
\subsection{Outlier characterization with a Multivariate Gaussian Model}

>>>>

This corresponds to a pair number density of $8 \times10^{-6}$ pairs
Mpc$^{-3}$, this is a factor $2.4$ lower than the pair number density
we find in Illustris-1.
There were a total of 146 pairs that met those criteria, but only $12$
were chosen for resimulation. 
Additionally, the selected pairs for resimulation have a relative
tangential velocity less than $75$ \kms. 
In this paper we only use the results from the $12$ resimulated pairs.

@@

We compare every satellite distribution against its own spherically
randomized distribution.
We keep fixed the radial position of every satellite
with respect to the central galaxy and then randomizing its angular
position. 
We repeat this procedure 1000 times for each satellite distribution
and proceed to measure the quantities mentioned in the last section:
$w$, $c/a$, $b/a$ and $\mu$.
For each quantity we compute an average and standard deviation from
the 1000 random samples. 
This allows us to build a normalized version of all quantities of
interest by substracting the mean and dividing between the standard
deviation of the randomized samples.

@@

\subsection{Multivariate Distributions}

\begin{table*}
  \centering
  \begin{tabular}{c|c|c|c|c|c|c|}
    \hline
        & M31 & M31 &M31 & MW & MW &MW\\
        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
M31 $w$ & & & & & & \\ 
M31 $c/a$ & & & & & & \\ 
M31 $b/a$ & & & & & & \\ 
MW $w$ & & & & & & \\ 
MW $c/a$ & & & & & & \\ 
MW $b/a$ & & & & & & \\ 
  \end{tabular}
  \begin{tabular}{c|c|c|c|c|c|c|}
    \hline
        & M31 & M31 &M31 & MW & MW &MW\\
        & $w$ & $c/a$ & $b/a$ & $w$ & $c/a$ & $b/a$ \\     \hline
M31 $w$ & & & & & & \\ 
M31 $c/a$ & & & & & & \\ 
M31 $b/a$ & & & & & & \\ 
MW $w$ & & & & & & \\ 
MW $c/a$ & & & & & & \\ 
MW $b/a$ & & & & & & \\ 
  \end{tabular}

  \caption{Correlation matrix for the normalized values of $w$, $c/a$
    and $b/a$ computed from the $20$ pairs in the Illustris-1
    simulation (left) and the ELVIS project (right).}
\end{table*}

\section{Discussion}

@@

\section{Discussion}

\subsection{Outlier characterization with a Multivariate Gaussian Model}
